Eagle: multi-locus association mapping on a genome-wide scale made routine

### 2019-08-07 BioinformaticsRevison/bioinformaticspaper.tex
Adding FarmCPU discussion point

>>>>

FarmCPU (ref) is a multi-locus association mapping method that was brought to our attention 
by a reviewer.  Unlike other LMM-based methods, it makes use of  two separate models for analysis, a fixed effect model and 
a random effect model.  The fixed effect model measures the strength of association between the SNPs and trait. 
This is done on a locus-by-locus basis but the model includes psuedo quantitative trait nucleotides (QTN), making it a multi-locus model. 
The random effect model is used to search for the optimal number and  size of "bins".  By "binning" the SNP data and identifying the 
SNP within a bin with the highest p-value (which is obtained from the fixed effect model), psuedo QTN are identified and feed back into the fixed effect model. The procedure stops 
once the number and size of the bins stabilises.

We analysed the mouse data with FarmCPU.

By "binning" the SNP data based on map location,

The 
random effect model identifies the optimal set of psuedo quantitiative trait nucleotides. The method is cyclic. Findings from the fixed effect model

This is done on a locus-by-locus basis but the model includes psuedo quantitative trait nucleotides, making it a multi-locus model. 
The random effect model contains a random effect and residual. The covariance matrix for the random effect is formed from

After completing our analyses, a new and different multi-locus method became available, FarmCPU (ref). 
FarmCPU is an iterative procedure, built around the repeated fitting of two models, a fixed effect model and a random effect model.

The fixed effect model measures the strength of association of a SNP with a trait, on a locus by locus basis. It controls for false positives 
by including QTNs as additional fixed effects.  The random effects model

is then used to optimize the binning of the genome

One a p value has been obtained for the SNPs,

The fixed effect model measures the statistical significance of the association between a SNP and trait. 
 It does this on a locus-by-locus basis.  Based on the SNPs significance and genome LD structure ,

The fixed effect model is fitted on a locus-by-locus basis. It contains the SNP effect and any identified QTNs.

The fixed effect model contains any identified QTNs

It is an iterative approach. At each iteration, a fixed effect and random effect model are fitted. The fixed effect model is fitted on a 
locus-by-locus basis. This can be done efficiently because the model only contains fixed effects.

 It is based on the fitting of two models, a fixed effect model and a random effect model. 
The fixed effect model is used to identify SNP in association with the trait. The random effect model is used to fine-tune the 
number of QTN.

The fixed effect model is fitted on a locus-by-locus basis. It contains quantitative trait nucleotides (QTNs) and

 It is build around two models, a fixed effect model and a random effect model.

FarmCPU is an iterative algorithm where for each iteration, both a fixed effect and random effect model are fitted. 
Single marker tests are performed with the fixed effect model.

The fixed effect model

While preparing our manuscript, a promising new multi-locus association mapping method became available, FarmCPU (ref).

During the course of preparing our manscript, three new multi-locus associaiton mapping methods became available. These are

While preparing our manuscript, three new multi-locus association mapping methods became available. These are 
mrMLM, FarmCPU, and BLINK.  mrMLM is an R package and available from CRAN, FarmCPU is written in R but is not in package form,  and 
BLINK is available in R or as stand alone C code.
